CA Affordabulity

### 2020-09-21 paper.Rmd
update

# census_vars2 <- c(median_income="B19013_001",
#                  pop_in_hh_with_income_assistance="B09010_002",
#                  pop_in_hh_with_no_income_assistance="B09010_008",
#                  hh_inc_5k="B19001_002",
#                  hh_inc_12.5k="B19001_003",
#                  hh_inc_17.5k="B19001_004",
#                  hh_inc_22.5k="B19001_005",
#                  hh_inc_27.5k="B19001_006",
#                  hh_inc_32.5k="B19001_007",
#                  hh_inc_37.5k="B19001_008",
#                  hh_inc_42.5k="B19001_009",
#                  hh_inc_47.5k="B19001_010",
#                  hh_inc_55k="B19001_011",
#                  hh_inc_67.5k="B19001_012",
#                  hh_inc_87.5k="B19001_013",
#                  hh_inc_112.5k="B19001_014",
#                  hh_inc_137.5k="B19001_015",
#                  hh_inc_175k="B19001_016",
#                  hh_inc_gr200k="B19001_017",
#                  hh_income_count = "B19001_001")

bg <- get_acs(state = "CA", geography = "block group",
                  variables = census_vars, geometry = TRUE)

@@

b.x <- st_buffer(st_transform(bounds,3310),dist=0)
t.x <- tracts %>%
  select(GEOID,geometry) %>%
  st_transform(3310) %>%
  st_buffer(dist=0) %>%
  mutate(AreaTract = st_area(.))

  st_buffer(st_transform(tracts,3310),dist=0)
bg.x <- st_buffer(st_transform(bg,3310),dist=0)
t.x$AreaTract_Total <- st_area(t.x)
bg.x$AreaBlockGroup_Total <- st_area(bg.x)

tracts.bounds <- st_intersection(b.x,t.x) 
tracts.bounds$Area_TractPWS <- st_area(tracts.bounds)
tracts.bounds$Percent_TractinPWS <- tracts.bounds$Area_TractPWS/tracts.bounds$AreaTract_Total

@@

### Find 20% and 50% Income quintile ranges by CWS (use block groups)

>>>>

census_vars2 <- c(median_income="B19013_001",
                 pop_in_hh_with_income_assistance="B09010_002",
                 pop_in_hh_with_no_income_assistance="B09010_008",
                 hh_inc_5k="B19001_002",
                 hh_inc_12.5k="B19001_003",
                 hh_inc_17.5k="B19001_004",
                 hh_inc_22.5k="B19001_005",
                 hh_inc_27.5k="B19001_006",
                 hh_inc_32.5k="B19001_007",
                 hh_inc_37.5k="B19001_008",
                 hh_inc_42.5k="B19001_009",
                 hh_inc_47.5k="B19001_010",
                 hh_inc_55k="B19001_011",
                 hh_inc_67.5k="B19001_012",
                 hh_inc_87.5k="B19001_013",
                 hh_inc_112.5k="B19001_014",
                 hh_inc_137.5k="B19001_015",
                 hh_inc_175k="B19001_016",
                 hh_inc_gr200k="B19001_017",
                 hh_income_count = "B19001_001")

bg <- get_acs(state = "CA", geography = "block group",
                  variables = census_vars2, geometry = TRUE)

@@

b.x <- st_buffer(st_transform(bounds,3310),dist=0)
t.x <- tracts %>% filter(variable=="median_income") %>%
  select(GEOID,NAME,geometry) %>%
  st_transform(3310) %>%
  st_buffer(dist=0) %>%
  mutate(AreaTract = st_area(.))

tracts.bounds <- st_intersection(b.x,t.x) 
tracts.bounds$Area_TractPWS <- st_area(tracts.bounds)
tracts.bounds$Percent_TractinPWS <- tracts.bounds$Area_TractPWS/tracts.bounds$AreaTract

@@

### Find 20% and 50% Income quintile ranges by CWS (use block groups)
tract.income <- tracts %>% filter(variable %in% c('hh_inc_5k',
                 'hh_inc_12.5k',
                 'hh_inc_17.5k',
                 'hh_inc_22.5k',
                 'hh_inc_27.5k',
                 'hh_inc_32.5k',
                 'hh_inc_37.5k',
                 'hh_inc_42.5k',
                 'hh_inc_47.5k',
                 'hh_inc_55k',
                 'hh_inc_67.5k',
                 'hh_inc_87.5k',
                 'hh_inc_112.5k',
                 'hh_inc_137.5k',
                 'hh_inc_175k',
                 'hh_inc_gr200k')) %>%
  st_drop_geometry() %>% group_by(GEOID) %>%
  mutate(cum_inc_sum = cumsum(estimate),
         percentile_inc = 100*cum_inc_sum/sum(estimate))
